Improving Coconut Rhinoceros Beetle Breeding Site Detection Using Harmonic Radar

### 2021-09-30 FS-CRB-HR-report2.tex
added rept 2

\begin{document}
\titlehead{US Forest Service Forest Health Protetion Grant Progess Report 1}
\title{Improving Coconut Rhinoceros Beetle Breeding Site Detection Using Harmonic Radar}
\author{Aubrey Moore, University of Guam}
%\date{Submitted December 30, 2020\\Revised January 28, 2021}
\maketitle
\begin{description}	
	\item[GRANTEE:] Aubrey Moore, University of Guam 
	\item[GRANT YEAR:] 2020
	\item[GRANT NUMBER:] 20-DG-11052021-227
	\item[GRANT PROGRAM:] Forest Health Protection
	\item[GRANT EXPIRATION DATE:] 2021-05-30
	\item[DATES COVERED BY THIS REPORT:] 2020-06-17 through 2020-12-31
	\item[GRANT STATUS:] Active
\end{description}

\begin{footnotesize}
\url{https://github.com/aubreymoore/Harmonic-Radar/raw/master/FS-CRB-HR-report1.pdf}
\end{footnotesize}

@@

\newpage
\listoftodos

@@

The most important activity is \textbf{Conduct field releases and tracking of tagged CRB (two week intensive fieldwork period)}. The intensive fieldwork will be performed on Guam in collaboration with Matt Siderhurst's team of students who have experience in tracking insects with harmonic radar. (We are following an approach similar to what we did in the radio-tracking feasibility study). This fieldwork activity has not yet been scheduled because of COVID-19 travel restrictions \ref{impediments}. Otherwise we are prepared to proceed.

@@

\label{impediments}
\section{PROBLEMS ENCOUNTERED THIS REPORTING PERIOD}

@@

>>>>

\begin{document}
\titlehead{US Forest Service Forest Health Protetion Grant Progess Report 2}
\title{Improving Coconut Rhinoceros Beetle Breeding Site Detection Using Harmonic Radar}
\author{Aubrey Moore, University of Guam}
%\date{Submitted December 30, 2020\\Revised January 28, 2021}
\maketitle
\begin{description}	
	\item[GRANTEE:] Aubrey Moore, University of Guam 
	\item[GRANT YEAR:] 2020
	\item[GRANT NUMBER:] 20-DG-11052021-227
	\item[GRANT PROGRAM:] Forest Health Protection
	\item[GRANT EXPIRATION DATE:] 2022-12-31 (extended)
	\item[DATES COVERED BY THIS REPORT:] 2021-01-01 through 2021-06-01
	\item[GRANT STATUS:] Active
\end{description}

\begin{footnotesize}
\url{https://github.com/aubreymoore/Harmonic-Radar/raw/master/FS-CRB-HR-report2.pdf}
\end{footnotesize}

@@

% TODO: \usepackage{graphicx} required
\begin{figure}
	\centering
	\includegraphics[width=0.7\linewidth]{drone}
	\caption{RECCO harmonic radar device suspended from an agricultural drone.}
	\label{fig:drone}
\end{figure}

\listoftodos

@@

The most important activity is to conduct field releases and tracking of tagged CRB over a two week intensive fieldwork period. The intensive fieldwork will be performed on Guam in collaboration with Matt Siderhurst's team of students who have experience in tracking insects with harmonic radar. (We are following an approach similar to what we did in the radio-tracking feasibility study). This fieldwork activity has not yet been scheduled because of COVID-19 travel restrictions (See section \ref{impediments} for details.). Otherwise we are prepared to proceed.

\subsection{Methods Development}

\textbf{The RECCO hand-held harmonic radar device we are using is designed for ground-based location of tags. We are collaborating with Dr. Glenn Dulla, Guam Department of Agriculture, to test the idea of mounting the device on a drone to allow efficient downward-looking scans over large areas. The idea is to mount the RECCO device on a drone which is programmed to fly a defined search path. A digital recorder cabled to the RECCO's headphone jack records the audio signal from the device and the drone's GPS  records location. Georeferencing is done by matching timestamps in the audio recording with timestamps in the GPS data. Postprocessing generates a map of signal strength with peaks indicating probable tag locations requiring confirmation by ground searches.
}

\textbf{Preliminary tests are promising. To date we have:
\begin{itemize}
	\item Used digital recordings of the RECCO's audio output to locate tags (Technical report)
	\item Flown the RECCO harmonic radar to a drone (Fig. \ref{fig:drone})
\end{itemize}
}

@@

\section{PROBLEMS ENCOUNTERED THIS REPORTING PERIOD}
\label{impediments}

@@

\textbf{COVID travel restrictions during the current reporting period did not allow Dr. Siderhurst and students to visit Guam to perform the planned field work. Guam is currently experiencing high COVID incidence predominantly caused by the D variant. We are currently targeting spring break 2022 as the time period for field work.}
